An equivalence of compositional frameworks

### 2019-05-30 EquivCompFrameworks_20180911kc.tex
added some definitions to the appendix and commented some stuff out

\begin{comment}
\section{Introduction}
Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary. Applied category theory provides such an avenue and much work has been done towards this effort  \cite{BC,BCR,BF,BFP,BP,Cour,Fong,JM,LS,Yass}. One of the more recent frameworks developed that is suitable for studying networks is Fong's `decorated cospans' \cite{Fong}. A $\textbf{cospan}$ in any category is a diagram of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (C) at (2,0) {$a_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $b$ the $\textbf{apex}$ of the cospan and $a_1$ and $a_2$ the $\textbf{feet}$ of the cospan. The morphisms $i$ and $o$ are called the $\textbf{legs}$. Cospans are ideal for realizing networks and more generally `open' systems where here open means that each system or network comes with prescribed inputs and outputs which are represented by the feet of the cospan $a$ and $b$, respectively. Two open systems viewed as cospans such that the outputs of the first and the inputs of the second coincide can then naturally be composed via pushout to obtain an open system whose inputs are that of the first and outputs are that of the second. For example, we can compose the above cospan with the following:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_2$};
\node (B) at (1,1) {$b^\prime$};
\node (C) at (2,0) {$a_3$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i^\prime$} (B)
(C) edge node[above]{$o^\prime$} (B);
\end{tikzpicture}
\]
to obtain a new cospan whose left foot is the left foot of the first, whose right foot is the right foot of the second, and whose apex and legs are given by the pushout.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,1) {$b^\prime$};
\node (E) at (4,0) {$a_3$};
\node (F) at (2,2) {$b+_{a_2} b^\prime$};
\node (G) at (2,1) {$b+b^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node[above]{$i^\prime$} (D)
(E) edge node[above]{$o^\prime$} (D)
(B) edge node[left]{$\psi j_b$} (F)
(D) edge node[right]{$\psi j_{b^\prime}$} (F)
(B) edge node[above]{$j_b$} (G)
(D) edge node[above]{$j_{b^\prime}$} (G)
(G) edge node [left] {$\psi$} (F);
\end{tikzpicture}
\]

@@

\subsection*{Acknowledgements}
Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
\end{comment}

@@

@@

@@

\begin{thm}
Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \colon EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\mathsf{A}$};
\node (B) at (1,0) {$\mathbf{Cat}$};
\node (C) at (0,-1) {$\mathsf{A^\prime}$};
\node (D) at (1,-1) {$\mathbf{Cat}$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F^\prime$} (D);
\end{tikzpicture}
\]
\end{thm}

@@

%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F^\prime(H(c_1+_b c_2))$. On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
\end{comment}

@@

The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:

@@

\begin{comment}
\section{Applications}\label{Applications}
In this section we present several examples each of which may be realized in the context of decorated cospans or in the context of structured cospans. The first example regarding graphs was mentioned in the introduction and used as a reoccurring theme throughout the paper. The next three examples which take on more of an applied flavor, consists of electrical circuits, Markov processes and Petri nets. Each of these has been studied extensively by Baez, Fong, Master and Pollard by way of `black-boxing' \cite{BCR,BF,BFP,BM,BP}. Black-boxing is a way of interpreting the behavior of an open system, that is, a system with prescribed inputs and outputs such as the terminals of an electrical circuit, by observing the activity at the inputs and the outputs. The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathsf{LinRel}$ of finite dimensonal vector spaces and linear relations. Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \colon \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \colon \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \colon \mathsf{Petri} \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal. The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans. The last two of these were also extended by being realized as double functors between double categories in recent works \cite{BC,BM}.
\subsection{Graphs}
As a first example that was also mentioned in the introduction, let $L \colon \mathsf{Set} \to \mathsf{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices. Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \colon \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \colon \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$. Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
\begin{enumerate}
\item{sets as objects,}
\item{functions as vertical 1-morphisms,}
\item{cospans of graphs, or, \emph{open} graphs of the form
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N)$};
\node (B) at (1,0) {$G$};
\node (C) at (2,0) {$L(M)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
as horizontal 1-cells, where $L(N)$ and $L(M)$ are discrete graphs on the sets $N$ and $M$, respectively, $G$ is a graph and $I$ and $O$ are graph morphisms, and}
\item{maps of cospans of graphs of the form
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,0) {$G_1$};
\node (C) at (2,0) {$L(M_1)$};
\node (A') at (0,-1) {$L(N_2)$};
\node (B') at (1,-1) {$G_2$};
\node (C') at (2,-1) {$L(M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I_1$} (B)
(C) edge node[above]{$O_1$} (B)
(A') edge node[above]{$I_2$} (B')
(C') edge node[above]{$O_2$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs induced by the underlying functions $f$ and $g$, respectively, and $\alpha \colon G_1 \to G_2$ is a graph morphism.
}
\end{enumerate}

@@

\begin{comment}
\section{Appendix}
Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:

@@

>>>>

%\begin{comment}
\section{Introduction}
Networks are playing an increasingly prominent role in our understanding of the world and as a result, methods of characterizing and studying networks have become evermore necessary. Applied category theory provides such an avenue and much work has been done towards this effort  \cite{BC,BCR,BF,BFP,BP,Cour,Fong,JM,LS,Yass}. One of the more recent frameworks developed that is suitable for studying networks is Fong's `decorated cospans' \cite{Fong}. A $\textbf{cospan}$ in any category is a diagram of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (C) at (2,0) {$a_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
We call $b$ the $\textbf{apex}$ of the cospan and $a_1$ and $a_2$ the $\textbf{feet}$ of the cospan. The morphisms $i$ and $o$ are called the $\textbf{legs}$. Cospans are ideal for realizing networks and more generally `open' systems where here open means that each system or network comes with prescribed inputs and outputs which are represented by the feet of the cospan $a$ and $b$, respectively. Two open systems viewed as cospans such that the outputs of the first and the inputs of the second coincide can then naturally be composed via pushout to obtain an open system whose inputs are that of the first and outputs are that of the second. For example, we can compose the above cospan with the following:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_2$};
\node (B) at (1,1) {$b^\prime$};
\node (C) at (2,0) {$a_3$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i^\prime$} (B)
(C) edge node[above]{$o^\prime$} (B);
\end{tikzpicture}
\]
to obtain a new cospan whose left foot is the left foot of the first, whose right foot is the right foot of the second, and whose apex and legs are given by the pushout.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,1) {$b$};
\node (C) at (2,0) {$a_2$};
\node (D) at (3,1) {$b^\prime$};
\node (E) at (4,0) {$a_3$};
\node (F) at (2,2) {$b+_{a_2} b^\prime$};
\node (G) at (2,1) {$b+b^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(C) edge node[above]{$i^\prime$} (D)
(E) edge node[above]{$o^\prime$} (D)
(B) edge node[left]{$\psi j_b$} (F)
(D) edge node[right]{$\psi j_{b^\prime}$} (F)
(B) edge node[above]{$j_b$} (G)
(D) edge node[above]{$j_{b^\prime}$} (G)
(G) edge node [left] {$\psi$} (F);
\end{tikzpicture}
\]

@@

\subsection*{Acknowledgements}
Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
%\end{comment}

@@

\textbf{Kenny: We should try to make this theorem shorter.}

@@

%\begin{comment}

@@

\begin{thm}
Given two finitely cocomplete categories $\mathsf{A}$ and $\mathsf{A}'$, two symmetric lax monoidal pseudofunctors $F \colon \mathsf{A} \to \mathbf{Cat}$ and $F' \colon \mathsf{A}' \to \mathbf{Cat}$, a finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A}'$, a symmetric lax monoidal pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ and a 2-isomorphism $\theta \colon EF \Rightarrow F^\prime H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F'\mathbb{C}\textnormal{sp}$ as defined above.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\mathsf{A}$};
\node (B) at (1,0) {$\mathbf{Cat}$};
\node (C) at (0,-1) {$\mathsf{A^\prime}$};
\node (D) at (1,-1) {$\mathbf{Cat}$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F^\prime$} (D);
\end{tikzpicture}
\]
\end{thm}

@@

%is given by $$1 \to F(c_1) \times F(c_2) \xrightarrow{} F(c_1 + c_2) \xrightarrow{} F(c_1 + _b c_2)$$ and then applying the functor $E$ results in $1 \to E(F(c_1+_b c_2))$, which by the comutative square is the same as $1 \to F^\prime(H(c_1+_b c_2))$. On the other hand, applying the functor $E$ to each decoration results in $$1 \to E(F(c_1)) \times E(F(c_2)) \xrightarrow{} E(F(c_1) \times F(c_2)) \xrightarrow{} E(F(c_1+c_2)) \xrightarrow E(F(c_1+_b c_2)) \xrightarrow{} F^\prime(H(c_1 +_b c_2))$$
%end{comment}

@@

The isomorphisms $\delta$ and $\mu$ satisfy the left and right unitality squares, associativity hexagon and braiding square. \textbf{Kenny: I think this might be a good place to cut the monoidal stuff.} To see this, let $M_1,M_2$ and $M_3$ be horizontal 1-cells in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:

@@

%\begin{comment}
\section{Applications}\label{Applications}
In this section we present several examples each of which may be realized in the context of decorated cospans or in the context of structured cospans. The first example regarding graphs was mentioned in the introduction and used as a reoccurring theme throughout the paper. The next three examples which take on more of an applied flavor, consists of electrical circuits, Markov processes and Petri nets. Each of these has been studied extensively by Baez, Fong, Master and Pollard by way of `black-boxing' \cite{BCR,BF,BFP,BM,BP}. Black-boxing is a way of interpreting the behavior of an open system, that is, a system with prescribed inputs and outputs such as the terminals of an electrical circuit, by observing the activity at the inputs and the outputs. The semantics of the activity at an open system's inputs and outputs is typically described in a category such as $\mathsf{LinRel}$ of finite dimensonal vector spaces and linear relations. Thus, in each case, black-boxing results in functors such as: $$\blacksquare_1 \colon \mathsf{Circ} \to \mathsf{LinRel}$$ $$\blacksquare_2 \colon \mathsf{Mark} \to \mathsf{LinRel}$$ $$\blacksquare_3 \colon \mathsf{Petri} \to \mathsf{LinRel}.$$ Each of these black-boxing functors also possess other convenient properties such as being symmetric monoidal. The first two of these were first done using Fong's theory of decorated cospans and then extended by the first two authors using structured cospans. The last two of these were also extended by being realized as double functors between double categories in recent works \cite{BC,BM}.
\subsection{Graphs}
As a first example that was also mentioned in the introduction, let $L \colon \mathsf{Set} \to \mathsf{Graph}$ be the functor that assigns to a set $N$ the \emph{discrete graph} on $N$ which is the edgeless graph $L(N)$ with no edges and $N$ as its set of vertices. Both $\mathsf{Set}$ and $\mathsf{Graph}$ are cocartesian monoidal and the functor $L \colon \mathsf{Set} \to \mathsf{Graph}$ is left adjoint to the forgetful functor $R \colon \mathsf{Graph} \to \mathsf{Set}$ which assigns to a graph $G$ its underlying set of vertices $U(G)$. Using structured cospans and appealing to Theorem \ref{SC}, we get a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{Graph})$ which has:
\begin{enumerate}
\item{sets as objects,}
\item{functions as vertical 1-morphisms,}
\item{cospans of graphs, or, \emph{open} graphs of the form
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N)$};
\node (B) at (1,0) {$G$};
\node (C) at (2,0) {$L(M)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
as horizontal 1-cells, where $L(N)$ and $L(M)$ are discrete graphs on the sets $N$ and $M$, respectively, $G$ is a graph and $I$ and $O$ are graph morphisms, and}
\item{maps of cospans of graphs of the form
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(N_1)$};
\node (B) at (1,0) {$G_1$};
\node (C) at (2,0) {$L(M_1)$};
\node (A') at (0,-1) {$L(N_2)$};
\node (B') at (1,-1) {$G_2$};
\node (C') at (2,-1) {$L(M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I_1$} (B)
(C) edge node[above]{$O_1$} (B)
(A') edge node[above]{$I_2$} (B')
(C') edge node[above]{$O_2$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
as 2-morphisms, where $L(f)$ and $L(g)$ are maps of discrete graphs induced by the underlying functions $f$ and $g$, respectively, and $\alpha \colon G_1 \to G_2$ is a graph morphism.
}
\end{enumerate}

@@

%\end{comment}

%\begin{comment}
\section{Appendix}
Before formally defining `pseudo double category', it is helpful to have the following picture in mind. A pseudo double category has 2-morphisms shaped like:

@@

\begin{defn}
Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories. A \define{lax double functor} is a functor $\mathbb{F} \colon\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$. This means that we have functors $\mathbb{F}_0 \colon \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \colon \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$. As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.

Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \colon 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_{1} \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_{1},N_{2}) \colon \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_{1} \odot N_{2})$ (the composition comparison), in a coherent way. This means that the following diagrams commute.

\item For a horizontal composite, $\beta \odot \alpha$,

\begin{equation}\label{eq:square}
  \xymatrix@-.5pc{
    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_{1})} \ar@{}[dr]|{\mathbb{F}(\beta)}&
    \mathbb{F}(C) \ar[d] &
     &
    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_{1},N_{2})} \ar[d]_{1} &
    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_{1})} &
    \mathbb{F}(C) \ar[d]^{1} \\
    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_{1}&
    \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
    \mathbb{F}(C') \ar[d]^{1}&
    = &
    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_{1} \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
     &
    \mathbb{F}(C) \ar[d] \\
    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} & 
     & 
    \mathbb{F}(C') &
     &
    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} &
     &
    \mathbb{F}(C') \\
  }.
\end{equation}

\item For a horizontal 1-cell $N \colon A \to B$, the following diagrams are commutative (under horizontal composition).

\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$\mathbb{F}(N) \odot 1_{\mathbb{F}(A)}$};
\node (C) at (3,1) {$\mathbb{F}(N)$};
\node (A') at (1,-1) {$\mathbb{F}(N) \odot \mathbb{F}(1_{A})$};
\node (C') at (3,-1) {$\mathbb{F}(N \odot 1_{A})$};
\node (B) at (5,1) {$1_{\mathbb{F}(B)} \odot \mathbb{F}(N)$};
\node (B') at (5,-1) {$\mathbb{F}(1_{B}) \odot \mathbb{F}(N)$};
\node (D) at (7,1) {$\mathbb{F}(N)$};
\node (D') at (7,-1) {$\mathbb{F}(1_{B} \odot N)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1 \odot \phi_{A}$} (A')
(C') edge node[right]{$\mathbb{F} \rho$} (C)
(A) edge node[above]{$\rho_{\mathbb{F}(N)}$} (C)
(A') edge node[above]{$\phi(N,1_{A})$} (C')
(B) edge node[left]{$\phi_{B} \odot 1$} (B')
(B') edge node[above]{$\phi(1_{B},N)$} (D')
(B) edge node[above]{$\lambda_{\mathbb{F}(N)}$} (D)
(D') edge node[right]{$F \lambda$} (D);
\end{tikzpicture}
\]

\item For consecutive horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$, the following diagram is commutative.

 \[\xymatrix{
    (\mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_{1},N_{2}) \odot 1}
    & \mathbb{F}(N_{1}) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
    \mathbb{F}(N_{1} \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_{1} \odot N_{2},N_{3})} &
    \mathbb{F}(N_{1}) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_{1},N_{2} \odot N_{3})}\\
    \mathbb{F}((N_{1} \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
    \mathbb{F}(N_{1} \odot (N_{2} \odot N_{3}))}\]
\end{enumerate}
We say the double functor $\mathbb{F}$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
\end{defn}

\begin{defn}
\label{defn:monoidal_double_functor}
A \define{(strong) monoidal lax double functor} $\mathbb{F} \colon \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a lax double functor $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ such that
	\begin{itemize}
		\item $\mathbb{F}_0$ and $\mathbb{F}_1$ are monoidal functors, meaning that there exists

\begin{enumerate}
\item{an isomorphism $\epsilon \colon 1_{\lD} \to \mathbb{F}(1_{\lC})$}
\item{a natural isomorphism $\mu_{A,B} \colon \mathbb{F}(A) \otimes \mathbb{F}(B) \to \mathbb{F}(A \otimes B)$ for all objects $A$ and $B$ of $\lC$}
\item{an isomorphism $\delta \colon U_{1_{\lD}} \to \mathbb{F}(U_{1_{\lC}})$}
\item{a natural isomorphism $\nu_{M,N} \colon \mathbb{F}(M) \otimes \mathbb{F}(N) \to \mathbb{F}(M \otimes N)$ for all horizontal 1-cells $N$ and $M$ of $\lC$}
\end{enumerate}
such that the following diagrams commute: for objects $A,B$ and $C$ of $\lC$,
 \[\xymatrix{
    (\mathbb{F}(A) \otimes \mathbb{F}(B)) \otimes \mathbb{F}(C) \ar[r]^{\alpha^\prime}\ar[d]_{\mu_{A,B} \otimes 1}
    & \mathbb{F}(A) \otimes (\mathbb{F}(B) \otimes \mathbb{F}(C)) \ar[d]^{1 \otimes \mu_{B,C}}\\
    \mathbb{F}(A \otimes B) \otimes \mathbb{F}(C) \ar[d]_{\mu_{A \otimes B,C}} &
    \mathbb{F}(A) \otimes \mathbb{F}(B \otimes C) \ar[d]^{\mu_{A,B \otimes C}}\\
    \mathbb{F}((A \otimes B) \otimes C)\ar[r]^{\mathbb{F}\alpha} &
    \mathbb{F}(A \otimes (B \otimes C))}\]
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$\mathbb{F}(A) \otimes 1_{\lD}$};
\node (C) at (3,1) {$\mathbb{F}(A)$};
\node (A') at (1,-1) {$\mathbb{F}(A) \otimes \mathbb{F}(1_{\lC})$};
\node (C') at (3,-1) {$\mathbb{F}(A \otimes 1_{\lC})$};
\node (B) at (5,1) {$1_{\lD} \otimes \mathbb{F}(A)$};
\node (B') at (5,-1) {$\mathbb{F}(1_{\lC}) \otimes \mathbb{F}(A)$};
\node (D) at (7,1) {$\mathbb{F}(A)$};
\node (D') at (7,-1) {$\mathbb{F}(1_{\lC} \otimes A)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1 \otimes \epsilon$} (A')
(C') edge node[right]{$\mathbb{F}(r_{A})$} (C)
(A) edge node[above]{$r_{\mathbb{F}(A)}$} (C)
(A') edge node[above]{$\mu_{A,1_{\lC}}$} (C')
(B) edge node[left]{$\epsilon \otimes 1$} (B')
(B') edge node[above]{$\mu_{1_{\lC},A}$} (D')
(B) edge node[above]{$\ell_{\mathbb{F}(A)}$} (D)
(D') edge node[right]{$\mathbb{F}(\ell_{A})$} (D);
\end{tikzpicture}
\]
and for horizontal 1-cells $N_{1},N_{2}$ and $N_{3}$ of $\lC$,
 \[\xymatrix{
    (\mathbb{F}(N_{1}) \otimes \mathbb{F}(N_{2})) \otimes \mathbb{F}(N_{3}) \ar[r]^{\alpha^\prime}\ar[d]_{\nu_{N_{1},N_{2}} \otimes 1}
    & \mathbb{F}(N_{1}) \otimes (\mathbb{F}(N_{2}) \otimes \mathbb{F}(N_{3})) \ar[d]^{1 \otimes \nu_{N_{2},N_{3}}}\\
    \mathbb{F}(N_{1} \otimes N_{2}) \otimes \mathbb{F}(N_{3}) \ar[d]_{\nu_{N_{1} \otimes N_{2},N_{3}}} &
    \mathbb{F}(N_{1}) \otimes \mathbb{F}(N_{2} \otimes N_{3}) \ar[d]^{\nu_{N_{1},N_{2} \otimes N_{3}}}\\
    \mathbb{F}((N_{1} \otimes N_{2}) \otimes N_{3})\ar[r]^{\mathbb{F}\alpha} &
    \mathbb{F}(N_{1} \otimes (N_{2} \otimes N_{3}))}\]
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,1) {$\mathbb{F}(N_{1}) \otimes U_{1_{\lD}}$};
\node (C) at (3,1) {$\mathbb{F}(N_{1})$};
\node (A') at (0,-1) {$\mathbb{F}(N_{1}) \otimes \mathbb{F}(U_{1_{\lC}})$};
\node (C') at (3,-1) {$\mathbb{F}(N_{1} \otimes U_{1_{\lC}})$};
\node (B) at (5,1) {$U_{1_{\lD}} \otimes \mathbb{F}(N_{1})$};
\node (B') at (5,-1) {$\mathbb{F}(U_{1_{\lC}}) \otimes \mathbb{F}(N_{1})$};
\node (D) at (8,1) {$\mathbb{F}(N_{1})$};
\node (D') at (8,-1) {$\mathbb{F}(U_{1_{\lC}} \otimes N_{1})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1 \otimes \delta$} (A')
(C') edge node[right]{$\mathbb{F}(r_{N_{1}})$} (C)
(A) edge node[above]{$r_{\mathbb{F}(N_{1})}$} (C)
(A') edge node[above]{$\nu_{N_{1},U_{1_{\lC}}}$} (C')
(B) edge node[left]{$\delta \otimes 1$} (B')
(B') edge node[above]{$\nu_{U_{1_{\lC}},N_{1}}$} (D')
(B) edge node[above]{$\ell_{\mathbb{F}(N_{1})}$} (D)
(D') edge node[right]{$\mathbb{F}(\ell_{N_{1}})$} (D);
\end{tikzpicture}
\]

		\item $S\mathbb{F}_1= \mathbb{F}_0S$ and $T\mathbb{F}_1 = \mathbb{F}_0T$ are equations between monoidal functors, and
		\item the composition and unit comparisons $\phi(N_1,N_2) \maps \mathbb{F}_1(N_1) \odot \mathbb{F}_1(N_2) \to \mathbb{F}_1(N_1\odot N_2)$ and $\phi_A \maps U_{\mathbb{F}_0 (A)} \to \mathbb{F}_1(U_A)$ are monoidal natural transformations.
	\end{itemize}
The monoidal lax double functor is \define{braided} if $\mathbb{F}_0$ and $\mathbb{F}_1$ are braided monoidal functors and \define{symmetric} if they are symmetric monoidal functors, and lax monoidal or oplax monoidal if the isomorphisms and families of natural isomorphisms of items (1)-(4) above are merely morphisms and natural transformations going in the appropriate directions.
\end{defn}
%\end{comment}
